%% This document created by Scientific Notebook (R) Version 3.0


\documentclass[12pt,thmsa]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{sw20jart}

%TCIDATA{TCIstyle=article/art4.lat,jart,sw20jart}

%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Created=Mon Aug 19 14:52:24 1996}
%TCIDATA{LastRevised=Mon Feb 10 18:41:32 1997}
%TCIDATA{Language=American English}
%TCIDATA{CSTFile=Lab Report.cst}
%TCIDATA{PageSetup=72,72,72,72,0}
%TCIDATA{AllPages=
%F=36,\PARA{038<p type="texpara" tag="Body Text" >\hfill \thepage}
%}


\input{tcilatex}
\begin{document}


\section{Sixteenth International Olympiad, 1974}

\subsection{1974/1. }

Three players $A,B$ and $C$ play the following game: On each of three cards
an integer is written. These three numbers $p,q,r$ satisfy $0<p<q<r.$ The
three cards are shuffled and one is dealt to each player. Each then receives
the number of counters indicated by the card he holds. Then the cards are
shuffled again; the counters remain with the players.

This process (shuffling, dealing, giving out counters) takes place for at
least two rounds. After the last round, $A$ has $20$ counters in all, $B$
has $10$ and $C$ has $9.$ At the last round $B$ received $r$ counters. Who
received $q$ counters on the first round?

\subsection{1974/2. }

In the triangle $ABC,$ prove that there is a point $D$ on side $AB$ such
that $CD$ is the geometric mean of $AD$ and $DB$ if and only if
\[
\sin A\sin B\leq \sin ^{2}\frac{C}{2}.
\]

\subsection{1974/3. }

Prove that the number $\sum_{k=0}^{n}\binom{2n+1}{2k+1}2^{3k}$ is not
divisible by $5$ for any integer $n\geq 0.$

\subsection{1974/4. }

Consider decompositions of an $8\times 8$ chessboard into $p$
non-overlapping rectangles subject to the following conditions:

(i) Each rectangle has as many white squares as black squares.

(ii) If $a_{i}$ is the number of white squares in the $i$-th rectangle, then 
$a_{1}<a_{2}<\cdots <a_{p}$. Find the maximum value of $p$ for which such a
decomposition is possible. For this value of $p,$ determine all possible
sequences $a_{1},a_{2},\cdots ,a_{p}$.

\subsection{1974/5. }

Determine all possible values of
\[
S=\frac{a}{a+b+d}+\frac{b}{a+b+c}+\frac{c}{b+c+d}+\frac{d}{a+c+d}
\]

where $a,b,c,d$ are arbitrary positive numbers.

\subsection{1974/6. }

Let $P$ be a non-constant polynomial with integer coefficients. If $n(P)$ is
the number of distinct integers $k$ such that $(P(k))^{2}=1,$ prove that $%
n(P)-\deg (P)\leq 2,$ where $\deg (P)$ denotes the degree of the polynomial $%
P.$

\end{document}
